---
title: "Manhattan Prep"
author: "Brett Burk"
output: 
  pdf_document: 
    number_sections: false
    fig_height: 11
    fig_width: 8.5
geometry: margin=0.5in
header-includes:
  - \usepackage{graphicx}
  - \usepackage{hyperref}
  - \usepackage{xcolor}
  - \usepackage{setspace}
---


```{r load-in, warning = FALSE, message = FALSE, results = 'asis', quietly = TRUE}
library(knitr)
folder <- "E:\\Projects\\manhattanPrep\\"
# folder <- "C:\\Users\\bmburk\\Dropbox\\manhattanPrep\\"
api.key <- read.table(paste0(folder, "convertAPIKey"), header = F)[[1]]
wf <- read.csv(paste0(folder, "GMATraw.csv"), stringsAsFactors = FALSE)
names(wf)[1] <- "SID"
ques <- read.csv(paste0(folder, "GMATrawQues.csv"), stringsAsFactors = FALSE)
names(wf) <- gsub("InstructorFirstName", "name", ques[,2])
# convert_pdf(paste0(folder, "CodeSheet.pdf"), paste0(folder, "codesheetcsv.csv"), api_key = api.key)
cs <- read.csv(paste0(folder, "codesheetcsv.csv"), skip = 2, stringsAsFactors = FALSE)
```

All based around question #2

```{r light exploration, warning = FALSE, message = FALSE, results = 'asis', quietly = TRUE}
t.df <- data.frame(table(wf$`How would you rate your overall learning experience with Manhattan Prep?`))
t.df$Pct <- round((t.df$Freq/sum(t.df$Freq)) * 100, 2)
kable(t.df)
lowest.rating <- subset(wf, 
                    wf$`How would you rate your overall learning experience with Manhattan Prep?` <= 2)
higher.rating <- subset(wf, 
                    wf$`How would you rate your overall learning experience with Manhattan Prep?` > 2)
rating.df <- data.frame(overall = colMeans(wf[,2:34], na.rm = T), 
                        lowest = colMeans(lowest.rating[,2:34], na.rm = T), 
                        highest = colMeans(higher.rating[,2:34], na.rm = T))

rating.df$high.low.diffs <- rating.df$highest - rating.df$lowest

colMeans(rating.df)
apply(rating.df, 2, sd)

rating.df <- data.frame(question = substr(row.names(rating.df), 1, 30), rating.df)
row.names(rating.df) <- NULL


biggest.diff <- subset(rating.df, rating.df$high.low.diffs >= mean(rating.df$high.low.diffs) + 
                         sd(rating.df$high.low.diffs))
kable(biggest.diff)
smallest.diff <- subset(rating.df, rating.df$high.low.diffs <= mean(rating.df$high.low.diffs) - 
                         sd(rating.df$high.low.diffs))
kable(smallest.diff)
rating.df$overall.low.diffs <- rating.df$overall - rating.df$lowest
kable(rating.df)
```

has co-instructor?

26-33 'co'

removal of class recordings due ot edge cases
```{r model building, warning = FALSE, message = FALSE, results = 'asis', quietly = TRUE}
temp.wf <-  wf[,-c(1, 11, 24:38)]
temp.wf$'Has Coinstructor' <- ifelse(is.na(wf$`Co-Instructor Code`), 0, 1)
names(temp.wf)[1] <- 'y'
model1 <- lm(y ~ ., data = temp.wf)
quantile(summary(model1)$residuals)
summary(model1)$r.squared
summary(model1)$adj.r.squared
kable(data.frame(model1$coefficients))
plot(model1)
```

`Cares about my success`                                        0.120413   0.037837   3.182  0.00153 ** 
`How would you rate [InstructorFirstName]'s teaching overall?`  0.361658   0.068634   5.269 1.87e-07 ***
`Would you recommend [InstructorFirstName]?`                    0.169364   0.056115   3.018  0.00264 ** 
`Course slides`                                                 0.075334   0.028940   2.603  0.00945 ** 
Books                                                           0.160086   0.035457   4.515 7.54e-06 ***
`Online materials`                                              0.086097   0.033253   2.589  0.00984 ** 
`Guidance on enrollment options`                                0.087332   0.039704   2.200  0.02819 *  
`Payment & billing services`                                    0.098908   0.047544   2.080  0.03789 * 


```{r model tuning, warning = FALSE, message = FALSE, results = 'asis', quietly = TRUE}
temp.wf2 <-  temp.wf[,c(1, 7:12, 16:17)]
model2 <- lm(y ~ ., data = temp.wf2)
quantile(summary(model2)$residuals)
summary(model2)$r.squared
summary(model2)$adj.r.squared
kable(data.frame(model2$coefficients))
plot(model2)
kable(data.frame(anova(model2)))
```


    Promoters (score 9-10) are loyal enthusiasts who will keep buying and refer others, fueling growth.
    Passives (score 7-8) are satisfied but unenthusiastic customers who are vulnerable to competitive offerings.
    Detractors (score 0-6) are unhappy customers who can damage your brand and impede growth through negative word-of-mouth.

Subtracting the percentage of Detractors from the percentage of Promoters yields the Net Promoter Score

```{r net promoter modeling, warning = FALSE, message = FALSE, results = 'asis', quietly = TRUE}
wf2 <- wf
wf2[,2][wf2[,2] == 4] <- 'Prom'
wf2[,2][wf2[,2] == 3] <- 'Pass'
wf2[,2][wf2[,2] <= 2] <- 'Detr'
wf2 <- wf2[!is.na(wf2$`How would you rate your overall learning experience with Manhattan Prep?`),]
total.wf2 <- sum(table(wf2[,2]))
wf2.pcts <- round((table(wf2[,2])/total.wf2) * 100, 2)

net.promoter <- (wf2.pcts[3] - wf2.pcts[1])[[1]]

detr <- wf2[wf2[,2] == 'Detr',]
pass <- wf2[wf2[,2] == 'Pass',]
prom <- wf2[wf2[,2] == 'Prom',]



cat('  \\newpage  ')

for(curr.col in 3:37){
  if(exists("joined.df")) remove(joined.df)
  for(type.resp in unique(wf2[,2])){
    temp <- wf2[wf2[,2] == type.resp,]
    temp.df <- data.frame(table(temp[,curr.col]), stringsAsFactors = F)
    temp.df$Pct <- round((temp.df$Freq/sum(temp.df$Freq)) * 100, 2)
    names(temp.df)[2:ncol(temp.df)] <- paste(type.resp, names(temp.df[2:ncol(temp.df)]))
    cat("  \n  ")
    if(exists("joined.df")){
      joined.df <- data.frame(merge(joined.df, temp.df, by = "Var1", all = TRUE), stringsAsFactors = F)
    } else {
      joined.df <- temp.df
    }
  }
  names(joined.df)[1] <- "V1"
  
  joined.df <- joined.df[order(as.character(joined.df[,1])),]
  joined.df <- rbind(joined.df, 
                     data.frame(t(c('SUM', colSums(joined.df[,2:7], na.rm = T))))
                     )
  
  cat(names(wf2)[curr.col])
  print(kable(joined.df))
}

```

Detractors--Less likely to be in online, more likely to be in a workshop

