---
title: "Manhattan Prep"
author: "Brett Burk"
output: 
  pdf_document: 
    number_sections: false
    fig_height: 11
    fig_width: 8.5
geometry: margin=0.5in
header-includes:
  - \usepackage{graphicx}
  - \usepackage{hyperref}
  - \usepackage{xcolor}
  - \usepackage{setspace}
---


```{r load-in, warning = FALSE, message = FALSE, results = 'asis', quietly = TRUE}
library(pdftables)
library(knitr)
folder <- "E:\\Projects\\manhattanPrep\\"
# folder <- "C:\\Users\\bmburk\\Dropbox\\manhattanPrep\\"
api.key <- read.table(paste0(folder, "convertAPIKey"), header = F)[[1]]
wf <- read.csv(paste0(folder, "GMATraw.csv"), stringsAsFactors = FALSE)
names(wf)[1] <- "SID"
kable(head(wf)[,1:21], longtable = TRUE)
kable(head(wf)[,22:38], longtable = TRUE)
ques <- read.csv(paste0(folder, "GMATrawQues.csv"), stringsAsFactors = FALSE)
names(wf) <- ques[,2]
nrow(wf)
# convert_pdf(paste0(folder, "CodeSheet.pdf"), paste0(folder, "codesheetcsv.csv"), api_key = api.key)
cs <- read.csv(paste0(folder, "codesheetcsv.csv"), skip = 2, stringsAsFactors = FALSE)
cat(paste(1:nrow(ques), ques[,2], " \n"))
```

2:10 are instruction based
11:14 curriculum
15:16 Facility
17:23 Service
24 is Overall experience
25:26 corporate (26 Displays only if "Y" on #58)
27:34 is co-instructor
35 is Program Description
36 Instructor Code
37 Co-Instructor Code
38 is Test Brand (all GMAT in this sample)


```{r light exploration, warning = FALSE, message = FALSE, results = 'asis', quietly = TRUE}
# Checking for repeat students
sum(table(wf[,1]) >= 2)

library(knitr)
# Skip 1 for student ID
for(i in 2:ncol(wf)){
  # cat("--------------------------------------------------------  \n")
  cat(paste0(i, ". ", ques[i,2], " \n"))
  curr.t <- as.data.frame(table(wf[,i], exclude = NULL))
  new.t <- as.data.frame(t(curr.t$Freq))
  names(new.t) <- curr.t$Var1
  # 
  print(kable(new.t))
  cat(" \n")
}
```

2:34 is 1:4  
25:26 is 0:1  
36 is Lead instructor code  
37 co instructor code  

```{r exploration continues, warning = FALSE, message = FALSE, results = 'asis', quietly = TRUE}

ques.df <- data.frame(Question = ques[,2], Mean = c(NA, colMeans(wf[,2:34], na.rm = T), rep(NA, 4)))

print(kable(ques.df))

#program description--35
agg.df <- aggregate(wf[,c(2:35)], by = list(wf$`Program Description`), FUN = mean, na.rm = T, na.action = NULL)
agg.df <- as.data.frame(t(agg.df), stringsAsFactors = F)
agg.df <- cbind(row.names(agg.df), agg.df)
names(agg.df) <- agg.df[1,]
agg.df <- agg.df[-1,]
agg.df <- cbind(row.names(agg.df), agg.df)
agg.df[,1] <- substr(agg.df[,1], 1, 30)
row.names(agg.df) <- NULL
agg.df <- agg.df[,-2]
names(agg.df)[1] <- 'Question'

print(kable(agg.df))

wf[,c(2:24, 27:34)] <- sapply(wf[,c(2:24, 27:34)], function(x) as.numeric(as.character(x)))

wf$means <- NA
for(i in 1:nrow(wf)){
  wf$means[i] <- mean(as.numeric(wf[i,c(2:24, 27:34)]), na.rm = T, na.action = NULL)
}

means.df <- summary(wf$means)
means.df <- data.frame(t(unlist(lapply(1:6, function(x) means.df[[x]]))))
names(means.df) <- names(summary(wf$means))

print(kable(means.df))

low.means <- wf[wf$means <= 3.476,]

nrow(low.means)
nrow(low.means)/nrow(wf)

low.ques.df <- data.frame(Question = ques[,2], Mean = c(NA, colMeans(low.means[,2:34], na.rm = T), rep(NA, 4)))
```


Now lets look at teachers

```{r exploratio continues, warning = FALSE, message = FALSE, results = 'asis', quietly = TRUE}
unique.codes <- unique(c(wf$`Lead Instructor Code`, wf$`Co-Instructor Code`))
avgs <- numeric()
for(uc in unique.codes){

  ic <- wf[wf$`Lead Instructor Code` == uc | wf$`Co-Instructor Code` == uc,]
  ques.df <- data.frame(Question = ques[,2], Mean = c(NA, colMeans(ic[,2:34], na.rm = T), rep(NA, 4)))
  cat(" \n")
  uc.avg <- round(mean(ques.df$Mean, na.rm = T), 2)
  # cat(paste('Instructor Code: \\textbf{', uc, "} AVG: \\textbf{", uc.avg,"} \n"))
  avgs[length(avgs) + 1] <- uc.avg
  
  
  
  # print(kable(ques.df))
}

means.df <- summary(avgs)
means.df <- data.frame(t(unlist(lapply(1:6, function(x) means.df[[x]]))))
names(means.df) <- names(summary(wf$means))
# print(kable(means.df))

inst.df <- data.frame(Inst.Code = unique.codes, Avg = avgs)

# print(kable(inst.df[order(inst.df$Inst.Code),], row.names = FALSE))

```

PFGE: Poor/Fair/Good/Excellent  
CN/GN/GY/CY: Completely No/Generally No/Generally Yes/Completely Yes